An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-09 poly-embed-journal/poly-embed-journal.tex
Adding examples intuition for inconsistency

\raf{Follow-up paragraph on prev sentence using abstain as an example}

%% also interesting to use Sec 4 to verify proposed canonical links
\raft{Rework so emphasis is more on the general construction and less on testing a given link}
With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function.
Yet for some target problems, the search for consistent surrogates has been restricted to those accommodating a particular canonical link function, such as $k$ largest coordinates of the surrogate report in top-$k$ classification (\S~\ref{sec:top-k}).
Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$. \jessiet{Redundant from \S 4 but I think that's okay.  I like it in both spots}
Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.
If the given $\psi$ is indeed consistent, then it is $\epsilon$-separated for sufficiently small $\epsilon$, so one can always construct such a $\Psi$ and verify that $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
See \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.

>>>>

%% giving intuition for new figure
For example, \citet{ramaswamy2018consistent} propose the BEP surrogate, which embeds the discrete abstain loss (\S~\ref{sec:abstain}).
With the abstain loss in hand, it is easy to verify that the abstain-optimal report for any $p$ such that $\max_y p_y < 1/2$ is to ``abstain'' from predicting.
When juxtaposed with multiclass classification in Figure~\ref{fig:abstain-intuition-inconsistent}, one can observe that the BEP surrogate does not indirectly elicit, and therefore does not embed, the mode.
The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate inconsistency with respect to a target task.
\raf{Follow-up paragraph on prev sentence using abstain as an example}

\begin{figure}
	\begin{minipage}{0.4\linewidth}
	\input{tikz/abstain-intuition}
\end{minipage}
\hfill
\begin{minipage}{0.55\linewidth}
	\caption{Example demonstrating the BEP surrogate $L^{BEP}$ (\S~\ref{sec:abstain}) is not calibrated for multiclass classification, eliciting the mode.
	The level sets of $\prop{L^{BEP}}$ are given in solid black lines, while the level sets of the mode are given in dashed blue lines.
	To demonstrate non-calibration, one can pick distributions $p, p'$ in the center cell (blue) such that $\vec 0 = \prop{L^{BEP}}(p) = \prop{L^{BEP}}(p')$, but $\mode(p) \neq \mode(p')$.  In this case, it is unclear how one should define $\psi(\vec 0)$, since it will not link to the mode for either $p$ or $p'$.  Thus, there is no calibrated link for the mode if the entire center cell is viable \jessie{word choice?}.  Instead, one may recover calibration by restricting to a subset of $\simplex$.}
	\label{fig:abstain-intuition-inconsistent}
	\end{minipage}
\end{figure}

%% also interesting to use Sec 4 to verify proposed canonical links
\raft{Rework so emphasis is more on the general construction and less on testing a given link}
With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function.
Yet for some target problems, the search for consistent surrogates has been restricted to those accommodating a particular canonical link function, such as $k$ largest coordinates of the surrogate report in top-$k$ classification (\S~\ref{sec:top-k}).
Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$. 
Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.
If the given $\psi$ is indeed consistent, then it is $\epsilon$-separated for sufficiently small $\epsilon$, so one can always construct such a $\Psi$ and verify that $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
See \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.
